Do I Need to Model You in order to Learn With You?

### 2015-04-22 mutual-modeling.tex
Completed study 3

\paragraph{Study-specific questions} Our hypothesis about media richness is
rejected: the average \Model{A}{B}{emotions} was .62 ($SD = .28$) with the
audio+video condition and .71 ($SD = .19$) in the audio condition ($F=3.4, p:
0.065$). Our interpretation is that viewing what one's partner sees (shared
graphical editor) was, in this task, more important than seeing each
other~\citep{gaver1993one,anderson1997impact}.

\paragraph{Symmetry question} Regarding the main items, the mutual modelling of
emotions, the correlation is .25 or .36  \fixme{a reprendre avec - Patrick}

\paragraph{Triangle questions} \fixme{Check ($\Delta_2$)} For $\Delta_3$, if we
compute for each subject A, the correlation between the vectors of emotions in
\gmodel{B}{A} and the vector in \gmodel{C}{A}, and take the average across all
60 subjects, we obtain a high correlation of .66. This average is
about the same in the two conditions.

@@

\paragraph{Rectangle question} We cannot address the relationship ($\Delta_4$)
between self-and social accuracy here because we don't have an estimation of
self-accuracy: subjects describe their emotions but we have no way to check if
there are correct. However, by measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{B}, on a scale of 7,
is in average of 0.3 for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0-5$ for \emph{discated} versus $SD=.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large variations even with one
area  (perceiving emotions)\fxfatal{Paragraph to rewrite}.

@@

\fixme{TBD}
\fixme{Check si il faut modifier les resultats de la symmetries}

>>>>

\paragraph{Study-specific questions} Our hypothesis about media richness is
rejected: the average \Model{A}{B}{emotions} was .62 ($SD = .28$) with the
audio+video condition and 0.71 ($SD = 0.19$) in the audio condition ($F=3.4, p:
0.065$).

\paragraph{Symmetry question} We computed the absolute differences between
\gModel{A}{B} and \gModel{B}{A} over all subjects (3 values per triad, 20
triads) and averaged them. The average difference in the degrees of accuracy of
symmetrical models is 0.21 ($SD= 0.21$): pairs of subjects tend to assess the
emotions of each other with similar levels of accuracy.

\paragraph{Triangle questions} $\Delta_2$ is computed in a similar way as the average of
the absolute differences between \gModel{A}{C} and \gModel{B}{C} over the 60
subjects. The average difference is 0.17 ($SD= 0.19$), indicating that, inside a
triad, $A$ and $B$ tend to model $C$ in a similar way. For $\Delta_3$, the
average absolute difference between \gModel{C}{A} and \gModel{C}{B} over the 60
subjects is 0.22 ($SD= 0.12$), which means that a given subject tends to model
the two other member of the triad with a similar degree of accuracy, which
supports $\mathcal{H}_{1}$.

@@

\paragraph{Rectangle question} We cannot address the relationship ($\Delta_4$)
between self and social accuracy here because we do not have an estimation of
self-accuracy: subjects describe their emotions but we have no way to check if
there are correct. By measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{B}, on a scale of 7,
is 0.3 in average for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0.5$ for \emph{discated} versus $SD=0.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large variations even within one
area  (perceiving emotions).

@@

The results evidence that richer media does not automatically foster better
modelling, on the contrary: groups using only the audio modality to exchange
their views were able to build more accurate models of each others than groups
using both video and audio, which is especially surprising when modelling
emotions: one would expect that video feedback indeed help building a better
model of the emotions of the other. Our interpretation is that viewing what
one's partner sees (shared graphical editor) was, in this task, more important
than seeing each other~\citep{gaver1993one,anderson1997impact}.

In this study, the accuracy of mutual modelling between two peers tend to be
symmetrical, which supports the idea that the quality of modelling is primarily
building upon the social interaction. This is further supported by a low
averaged $\Delta_2$: if, for any $A$ and $B$, $A$ and $B$ generally model $C$
with a similar level of accuracy, it is likely due to the social interaction
induced by $C$ (hypothesis $\mathcal{H}_{2}$).

On the other hand, the low $\Delta_3$ that we also found ($C$ tends to always
model $A$ and $B$ with similar levels of accuracy) tend to contradict this, and
supports the idea that modelling is primarily an individual skill (hypothesis
$\mathcal{H}_{1}$).
